\sectionTitle{Experience}{}

\begin{experiences}

\researchexperience
    {Present}   {Microsoft Research | Center for Societal Impact through Cloud \& AI{\normalfont  ~ [\href{https://www.microsoft.com/en-us/research/collaboration/scai/}{\small{\websiteSymbol}}]
    }}{Bangalore, India}{Bangalore, India}
    {Jul 2019} {\textit{AI Center Fellow | Advisors:  \href{https://www.microsoft.com/en-us/research/people/kalikab/}{Dr. Kalika Bali}, \href{https://www.microsoft.com/en-us/research/people/monojitc/}{Dr. Monojit Choudhury}, \href{https://www.microsoft.com/en-us/research/people/taganu/}{Tanuja Ganu}}\\
    Working on understanding the disparity between research and deployment especially for low resource languages and developing technologies to mitigate this gap (``Language Technologies for All").
    \vskip 0.1cm

    }
\researchexperience
    {}   {}{}{}
    {Jan 2019} {\textit{Research Intern | Advisors:  \href{https://www.microsoft.com/en-us/research/people/kalikab/}{Dr. Kalika Bali}, 
    \href{https://www.microsoft.com/en-us/research/people/monojitc/}{Dr. Monojit Choudhury}
    }\\
    Developed Interactive Neural Machine Translation which assists translators with suggestions on-the-fly with the aim to bring forth a synergy between the pros of human and machine translation.
    }
  \emptySeparator
 \researchexperience
    {Dec 2018}   {Carnegie Mellon University | School of Computer Science}{Pittsburgh, USA}{}
    {Jul 2018} {\textit{Research Intern (Bachelor Thesis) | Advisor:  \href{http://www.cs.cmu.edu/~dst/}{Prof. Dave Touretzky}}\\
    Worked on real-time obstacle collision avoidance and doorway navigation with limited sensor capacity of monocular vision and low computational constraints. 
    }
  \emptySeparator
   \researchexperience
    {Jun 2018}   {University College London | Web Intelligence Group{\normalfont  ~ [\href{http://wi.cs.ucl.ac.uk/index.php/people/}{\small{\websiteSymbol}}]
    }}{London, UK}{}
    {May 2018} {\textit{Summer Research Intern | Advisors: \href{https://sites.google.com/site/emineyilmaz/}{Prof. Emine Yilmaz}, \href{http://rishabhmehrotra.com/}{Dr. Rishabh Mehrotra}}\\
    Worked on user tasks and needs understanding specifically on understanding how incorporating task information can lead to better, more relevant search/retrieval.
    }
  \emptySeparator
    \researchexperience
    {Aug 2018}   {NumFOCUS | Julia Computing{\normalfont  ~ [\href{https://numfocus.org/blog/google-summer-of-code-2018-julia-cohort}{\small{\websiteSymbol}}]
    }}{Remote}{}
    {May 2018} {\textit{Google Summer of Code 2018 | Mentor: \href{https://www.oxinabox.net/}{Dr. Lyndon White}}\\
    Developed DataDepsGenerators.jl, a provenance-preserving data preprocessing tool to generate executable metadata for published datasets. Added support to popular data repositories such as FigShare, Zenodo.
    }
  \emptySeparator
   \researchexperience
    {Aug 2017}   {Mozilla | Bugzilla Team {\normalfont  ~ [\href{https://wiki.mozilla.org/BMO}{\small{\websiteSymbol}}]
    }}{Remote / Austin, USA}{}
    {May 2017} {\textit{Google Summer of Code 2017 | Mentor: \href{https://www.linkedin.com/in/dylanwh/}{Dylan Hardison}}\\
    Worked on Bugzilla, a bug-tracking tool to introduce a new single page bug filing interface \href{https://bugzilla.mozilla.org/enter_bug.cgi}{enter\_bug.cgi} which replaced the previous interface based on conditional forms that required cumbersome navigation.
    }
  
\end{experiences}
\vspace{-4mm}
