% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\researchexperience
    {Starting}   {Microsoft Research, Bangalore, India}{}{}
    {January 2019} {\textit{Incoming Research Intern | Advisor:  \href{https://www.microsoft.com/en-us/research/people/kalikab/}{Kalika Bali}}\\
    Will be working in the intersection of NLP and ICTD, developing technologies for low-resource languages.}
  \emptySeparator
 \researchexperience
    {December 2018}   {Carnegie Mellon University, Pittsburgh, USA}{}{}
    {July 2018} {\textit{Research Intern (Senior Thesis) | Advisor:  \href{http://www.cs.cmu.edu/~dst/}{David Touretzky}}\\
    Working on real-time obstacle avoidance and doorway navigation using a monocular camera on a low-computational robot like Anki Cozmo.                                                        
                    }
  \emptySeparator
   \researchexperience
    {June 2018}   {University College London, London, UK}{}{}
    {May 2018} {\textit{Summer Research Intern | Advisors: \href{https://sites.google.com/site/emineyilmaz/}{Emine Yilmaz} and \href{http://www.rishabhmehrotra.com/}{Rishabh Mehrotra}}\\
                       Worked on Task-based Information Retrieval, specifically on recommendation by leveraging external ontology. Used the principles of Bayesian Rose Trees and Distance Dependent Chinese Restaurant Process to design a dynamically enriched ontology.
                        Worked on several research ideas documented at: \href{https://usercontext.github.io/}{UserContext}.
                     
                    }
  \emptySeparator
    \researchexperience
    {August 2018}   {Julia Computing (NumFOCUS)}{NumFOCUS}{Remote}
    {May 2018} {\textit{Google Summer of Code 2018 | Mentor: \href{https://white.ucc.asn.au/}{Lyndon White}}\\
    Added data repository support to DataDepsGenerators.jl, which in turn creates registration blocks for DataDeps.jl. DataDeps.jl helps in downloading scientific data with ease. Talk on this work delivered at PyData New York City 2018.
                    }
  \emptySeparator
   \researchexperience
    {August 2017}   {Mozilla Foundation (Bugzilla)}{}{Remote}
    {May 2017} {\textit{Google Summer of Code 2017 | Mentor: \href{https://www.linkedin.com/in/dylanwh}{Dylan Hardison}}\\
    Revamped the existing bug filing interface (enter\_bug.cgi) into a single page reducing the multi-hop db access and unnecessary template rendering. This enhanced the speed and performance in bug filing.
                    }
  
\end{experiences}
\vspace{-4mm}
